Profiles of Wind Veer and Wind Speed in Turbulent Ekman Flow

### 2023-05-22 write1/manuscript.tex
Data and modifications from 2022

\usepackage[margin=3.5cm]{geometry}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[footnotesize]{caption}
\usepackage{xcolor}
\usepackage{dirtytalk}
\usepackage{colortbl}
\usepackage{booktabs}

@@

\newcommand{\todo}[1]{\textcolor{red}{$[$#1$]$}}
\newcommand{\quotation}[1]{"#1"}

@@

Wind veer away from its geostrophic direction is
(i) due to direct frictional effects in the very vicinity of the surface and
(ii) due to turbulence which exerts indirect frictional effects; these effects
cause a slow-down of the mean wind reducing the Coriolis force thus turning the wind
in favor of the pressure gradient force. 
%%
Not only does the veering set the frame of reference for surface layer theory, it also has
effects at small and large scales from large-scale dispersion via plume spreading to
cyclone spin-down \citep{svensson:BM2009}
and on the capabilities of data assimilation and accuracy of surface flux estimates \citep{brown:QJR2005}. 
%
From a large-scale perspective, the veering of wind across the planetary boundary layer determines
the amount of cross-isobaric mass-flux, commonly referred to as 'Ekman pumping' \citep{ekman:AMA1905},
and it is thus a key factor in the life-cycle of large-scale synoptic systems.
%
% %% This shear is probably not related to Ekman-turning 
% On the mesoscale, shear in the surface layer a crucial factor for the initiation and sustainment of strong convective events (REFERENCE?).
% 
Within the atmospheric boundary layer (ABL), directional shear of the wind in
the upper part of the surface layer may cause a systmatic yaw for tall wind power generation devices
where blades reach into the Ekman layer, i.e. that part of the boundary layer where the wind starts to turn;
an exact estimate of such effects is critical in the site assessments for wind farms
\citep{calaf:PF2010, mirocha:WES2018}. 
%
\par
%
In the planetary boundary layer, wind veer is characterized by the surface veering angle $\alpha$
defined as the angle between the negative surface shear stress $\tau_\SFC$ and the geostrophic wind.
%
Surface veering $\alpha$ and geostrophic drag $Z\equiv u_\star/G$, where $u_\star\equiv\sqrt{\nu|\tau_\SFC|}$,
uniquely determine the surface drag $\tau_\SFC$ in a turbulent Ekman flow. 
%
In any quantitative description of the surface layer, the friction velocity $u_\star$ is the dynamic scale
and $\alpha$ defines the alignment of the frame of reference.
%
Knowledge about $u_\star$ and $\alpha$ is thus a pre-requisite for any quantitative theory of the surface layer, 
and \citet{rossby:PPO1935} constrained the two parameters based on integral relations in the ABL.
%
Asymptotic similarity theory was later used by \citet{tennekes:JAS1973, blackadar:JAS1968},
and--based on his seminal direct numerical simulations (DNS) of Ekman flow--,~\cite{spalart:JFM1989} suggested
a modification to take into account effects of low to intermediate Reynolds numbers.
Later on, constants were re-evaluated with a focus on the atmospheric boundary layer based on
observations \citep{hogstrom:BM1988,hogstrom:BM1996}
and numerical modelling \citep{spalart:PF2008, spalart:PF2009, ansorge:BM2014, ansorge:BM2019}.
\todo{Refer to Pena et al, 2010} 
%
\par
%
Attempts were also undertaken to obtain profiles of the wind speed: 
One approach is to match the inner and outer layer at a reference height;
\citet{etling:2002, emeis:2018}  (Sec. 21.10; Eq. 21.48) choose the Prandtl-layer height to match
the wind speed profiles, which, however, requires to externally prescribe the veering $\alpha$ at that height. 
A one-dimensional profile with constant veering is given by \citet[Sec. 3; Eq. 3.1-3.19]{emeis:m2007}.

@@

for instance when the wind speed needs to be evaluated at heights on the order of 100-200\,\mathrm{m},

@@

of \say{\emph{fully developed turbulence}  believed to occur for a sufficiently large but finite Reynolds number}

@@

  S_\mathrm{visc}= \nu \sqrt\left(\frac{\p U}{\p z}\right)^2  + \left(\frac{\p V}{\p z}\right)^2}

@@

  U_\text{inner}^{\alpha_\star}^+ = \frac{z^+}{1+c_1 (y^+)^2} +  (c_2 y^+ - a_\mathrm{match} )\frac{1+tanh\left[0.2(y^+-22)\right]}{2} + c_3 e^{-c_4(y^+-22)^2}. \label{eqn:u_inner} 

@@

  c_1 &=& 0.00185;\quad
  c_2 &=& 0.195;\quad 
  c_3 &=& 0.4 ; \quad
  c_4 &=& 0.35. 

@@

  U_\text{log}^{\alpha_\star}^+ = \frac{1}{\kappa} \log y^+ + C 

@@

  \left.\partial_{z^+} V^{\alpha_\star+}}\right|_{z=0} &=& 0.  

@@

\begin{figure}
  \phantom{AAA}\textbf{(a)\hspace{0.3\textwidth}(b)\hspace{0.3\textwidth}(c)}\\
  \includegraphics[width=\textwidth]{../plot/ekman_profiles.pdf}
  \caption{ \textbf{(a)} Velocity deficity, \textbf{(b)} velocity profile in shear-aligned hodographs and \textbf{(c)} hodograph in geostrophy-aligned coordinates.
    Thick, solid lines show theory, dashed lines data from DNS. }
  \label{fig:hodograph} 
\end{figure}

@@

\textbf{Compare} to Emeis (2002) and Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;
%
\par%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Implications for \textbf{K-theory} (we now can consider that shear and stress are not necessarily perfectly aligned).
$\rightarrow$ can we do something to infer a K-profile from these theoretical considerations? 
%
\begin{figure}
  \includegraphics[width=\textwidth]{../plot/mag_dir.pdf} 
  \caption{Total velocity and veering (in degrees) vs inner and outer height.
    Dashed lines show DNS data, thick lines are from semi-empirical theory.} 
\end{figure} 
%
\section{Conclusions}
%
Applications:
\begin{itemize}
\item reference-shear for neutral profile approaches(systematic!) $\rightarrow$ wind engineering! 
\item initial condition for LES/DNS to eliminate/minimize inertial oscillation in Benchmark simulations
\item
\end{itemize}

@@

\begin{subequations}
\begin{eqnarray}
  \left(\begin{matrix}
    \p_t U\\
    \p_t W  
  \end{matrix}\right)&=&\left(\begin{matrix}
     fW &+& \nu \p_z^2 U\\ 
    -f(U-G) &+& \nu \p_z^2 W
  \end{matrix}\right)\\ 
  \Rightarrow \partial_t (U+iW) &=& f(W-i(U-G))) + \nu \p_z^2(U+iW)
\end{eqnarray}
In stationary conditions, this system is solved by
\begin{eqnarray}
  \hat{u}(z) &=& U_{\infty} + e^{-\gamma z} \left[A \cos\gamma z + B \sin\gamma z\right]   \\
  \hat{w}(z) &=& W_{\infty} + e^{-\gamma z} \left[-A \sin\gamma z + B \cos\gamma z\right]
\end{eqnarray} 
\end{subequations}
where the constants $U_\infty$, $W_\infty$ set the top boundary condition and $A$ and $B$ set the bottom boundary condition. 
%
The most common boundary condition for a surface Ekman layer is $A=U_{\infty}=G$, $B=0$, and $W_{\infty}=0$.
%
The lower boundary condition, however, neglects the existence of the surface layer, and it appears reasonable to define
$A=c G$ where $c<1$ is a constant that icorporates the increased shear in the surface layer.
%
Given a 'matching height' $z_{match}$ and normalized matching height $\xi=\gamma z_\text{match}$ in the upper part of the inner layer, we can match the Ekman profile
to the inner layer by letting
%
\begin{eqnarray}
  \begin{matrix} 
    u(z_\text{match}) \equiv u_\text{match} &=& U_{\infty} + e^{-\gzm}} \left [ A \cos\gzm + B\sin\gzm \right] \\
    w(z_\text{match}) \equiv w_\text{match} &=& W_{\infty} + e^{-\gzm}} \left [-A \sin\gzm + B\cos\gzm \right]
  \end{matrix} 
\end{eqnarray}
\begin{eqnarray}
  \Rightarrow \left(\begin{matrix}
    u_\text{match}-U_{\infty} \\ 
    w_\text{match}-W_{\infty}
  \end{matrix}\right) = e^{-\gzm}\left(\begin{matrix}A \\ B \end{matrix}\right)\left(\begin{matrix}
    \cos\gzm &+ \sin\gzm \\ -\sin\gzm &+ \cos\gzm
  \end{matrix} \right) \\
\end{eqnarray}
Matching the profile at $\xi=0$, one obtains
$A = \Delta u_\text{match} $ and $B=-\Delta w_\text{match} $; and when the direction $Ox$ is aligned
with the geostrophic wind, we obtain the textbook-case $A=|\mathbf{G}|$ and $B=0$.

@@

\section{Matching the spanwise velocity profiles in the inner layer}
\label{app:log-coefficients}
The spanwise profile in vicinity of the surface is given by
$V/G=f_{V,\mathrm{visc}}\delta ^+$ with
\begin{subequations}
\begin{eqnarray}
  f_{V,\mathrm{visc}} &=& v_\mathrm{ref}\left(\omega_v z^+ -1 + e^{-\omega_v z^+}\right)\\
  f_{V,\mathrm{log}}   &=& a_\mathrm{log} + b_\mathrm{log} \log z^+ + c_\mathrm{log} z^+ 
\end{eqnarray}
\end{subequations}
Matching the profiles and gradient $z_0=10^+$ and the value at $z_1=0.3\dlta^+$ yields
\begin{subequations} 
\begin{eqnarray}
  v_\mathrm{ref} \left(\omega_v z_{0} + e^{-\omega_v z_{0}}\right)
  & = v_{0}=& a_\mathrm{log} + b_\mathrm{log} \log z_{0} +c_\mathrm{log} z_{0}  \\
  &   v_{1}=& a_\mathrm{log} + b_\mathrm{log} \log z_{1} +c_\mathrm{log} z_{1} \\
  v_\mathrm{ref}\omega_z \left( 1 - e^{-\omega_z z_{0}}\right)
  & = d_{0}=& \frac{b_\mathrm{log}}{z_{10}} + c_\mathrm{log} 
\end{eqnarray}
\end{subequations} 
The gradient condition implies $b_\mathrm{log}=(d_{0} -c_\mathrm{log})z_{0}$, and yields
\begin{subequations}
\begin{eqnarray}
  %v_{0}&=& a_\mathrm{log} + z_{0}\left[ (d_0-c_\mathrm{log}) \log z_{0} +c_\mathrm{log}\right]\\
  v_0-z_0d_0\log z_0&=& a_\mathrm{log} + c_\mathrm{log} (z_0- z_0\log z_0) \\
  %v_1 &=& a_\mathrm{log} + z_0(d_0-c_\mathrm{log})\log z_1 +  c_\mathrm{log}z_1\\ 
  v_1-z_0d_0\log z_1 &=& a_\mathrm{log} +c_\mathrm{log} (z_1- z_0\log z_0)  \\
  \Rightarrow c_\mathrm{log}&=& \frac{ \Delta v - z_0d_0 \log z_1/z_0}{\Delta z} 
\end{eqnarray}
with $\Delta z=z_1-z_0$ and $\Delta v=v_1-v_0$.
%
Then, the coefficient $a_\mathrm{log}$ is estimated as 
\begin{eqnarray} 
  a_\mathrm{log} &=& v_0-z_0d_0\log z_0 -  \frac{ \Delta v - z_0d_0 \log z_1/z_0}{\Delta z}\left[
    z_0-z_0\log z_0 
    \right]. 
\end{eqnarray}
We note that $ \log(z_1/z_0) / (z_1-z_0) \rightarrow 0$ for large $z_1$, and as $z_1=0.3\delta^+$,
this implies that the second term in $c_\mathrm{log}$ only plays a role at low and intermediate $\RE$.
Then, $a_\mathrm{log}$ can be estimated as 
\begin{eqnarray}
  a_\mathrm{log} \simeq v_0 -z_0 \left[ d_0 \log  z_0 - \frac{\Delta v}{\Delta z} ( 1- \log z_0) \right] 
\end{eqnarray}
for large $\RE$. 
\end{subequations}

@@

  \end{array} \right, 

@@

with $\Delta V &=& V_\text{outer}(z^-_\text{up})-V_\text{inner}(z^+_\text{low})$

@@

>>>>

\usepackage[margin=3.5cm]{geometry}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[footnotesize]{caption}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{booktabs}

@@

\newcommand{\todo}[1]{\textcolor{red}{$[$#1$]$}}
\renewcommand{\quotation}[1]{"#1"}

@@

Wind veer away from its geostrophic direction is
(i) due to direct frictional effects in the very vicinity of the surface and
(ii) due to turbulence which exerts indirect frictional effects; these effects
cause a slow-down of the mean wind reducing the Coriolis force thus turning the wind
in favor of the pressure gradient force. 
%%
Not only does the veering set the frame of reference for surface layer theory, it also has
effects at small and large scales from large-scale dispersion via plume spreading to
cyclone spin-down \citep{svensson:BM2009}
and on the capabilities of data assimilation and accuracy of surface flux estimates \citep{brown:QJR2005}. 
From a large-scale perspective, the veering of wind across the planetary boundary layer determines
the amount of cross-isobaric mass-flux, commonly referred to as 'Ekman pumping' \citep{ekman:AMA1905},
and it is thus a key factor in the life-cycle of large-scale synoptic systems.
% %% This shear is probably not related to Ekman-turning 
% On the mesoscale, shear in the surface layer a crucial factor for the initiation and sustainment of strong convective events (REFERENCE?).
Within the atmospheric boundary layer (ABL), directional shear of the wind in
the upper part of the surface layer may cause a systmatic yaw for tall wind power generation devices
where blades reach into the Ekman layer, i.e. that part of the boundary layer where the wind starts to turn;
an exact estimate of such effects is critical in the site assessments for wind farms
\citep{calaf:PF2010, mirocha:WES2018}. 
In the planetary boundary layer, wind veer is characterized by the surface veering angle $\alpha$
defined as the angle between the negative surface shear stress $\tau_\SFC$ and the geostrophic wind.
Surface veering $\alpha$ and geostrophic drag $Z\equiv u_\star/G$, where $u_\star\equiv\sqrt{\nu|\tau_\SFC|}$,
uniquely determine the surface drag $\tau_\SFC$ in a turbulent Ekman flow. 
In any quantitative description of the surface layer, the friction velocity $u_\star$ is the dynamic scale
and $\alpha$ defines the alignment of the frame of reference.
Knowledge about $u_\star$ and $\alpha$ is thus a pre-requisite for any quantitative theory of the surface layer, 
and \citet{rossby:PPO1935} constrained the two parameters based on integral relations in the ABL.
Asymptotic similarity theory was later used by \citet{tennekes:JAS1973, blackadar:JAS1968},
and--based on his seminal direct numerical simulations (DNS) of Ekman flow--,~\cite{spalart:JFM1989} suggested
a modification to take into account effects of low to intermediate Reynolds numbers.
Later on, constants were re-evaluated with a focus on the atmospheric boundary layer based on
observations \citep{hogstrom:BM1988,hogstrom:BM1996}
and numerical modelling \citep{spalart:PF2008, spalart:PF2009, ansorge:BM2014, ansorge:BM2019}.
\todo{Refer to Pena et al, 2010} 
Attempts were also undertaken to obtain profiles of the wind speed: 
One approach is to match the inner and outer layer at a reference height;
\citet{etling:2002, emeis:2018}  (Sec. 21.10; Eq. 21.48) choose the Prandtl-layer height to match
the wind speed profiles, which, however, requires to externally prescribe the veering $\alpha$ at that height. 
A one-dimensional profile with constant veering is given by \citet[Sec. 3; Eq. 3.1-3.19]{emeis:m2007}. 
%%% ADD REFERENCE TO Klein and Maier (PAMM, 2021) for failure of matching of profile in 1D ODT-LES
%%% ADD REFERENCE TO Lindevall and Svensson (QJRMS, 2019, vol 145)

@@

for instance when the wind speed needs to be evaluated at heights on the order of $100-200\,\mathrm{m}$,

@@

of \quotation{\emph{fully developed turbulence}  believed to occur for a sufficiently large but finite Reynolds number}

@@

  S_\mathrm{visc}= \nu \sqrt{\left(\frac{\p U}{\p z}\right)^2  + \left(\frac{\p V}{\p z}\right)^2}

@@

  U_\text{inner}^{{\alpha_\star}^+} = \frac{z^+}{1+c_1 (y^+)^2} +  (c_2 y^+ - a_\mathrm{match} )\frac{1+tanh\left[0.2(y^+-22)\right]}{2} + c_3 e^{-c_4(y^+-22)^2}. \label{eqn:u_inner} 

@@

  c_1 = 0.00185;\quad
  c_2 = 0.195;\quad 
  c_3 = 0.4 ; \quad
  c_4 = 0.35. 

@@

  {U_\text{log}^{\alpha_\star}}^+ = \frac{1}{\kappa} \log y^+ + C 

@@

  \left.\partial_{z^+} V^{\alpha_\star+}\right|_{z=0} &=& 0.  

@@

  \phantom{AAA}\textbf{(a)\hspace{0.3\textwidth}(b)\hspace{0.3\textwidth}(c)}\\
  \includegraphics[width=\textwidth]{../plot/ekman_profiles.pdf}
  \caption{ \textbf{(a)} Velocity deficity, \textbf{(b)} velocity profile in shear-aligned hodographs and \textbf{(c)} hodograph in geostrophy-aligned coordinates.
    Thick, solid lines show theory, dashed lines data from DNS. }
  \label{fig:hodograph} 

@@

\textbf{Compare} to Emeis (2002) and Gryning (2007); highlight explicit knowledge on veering-profile $\rightarrow$ directional sheer;

Consider Townsend ``Turbulent Shear Flow''  Chapter 7.18: p. 319 
%
\par%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
Implications for \textbf{K-theory} (we now can consider that shear and stress are not necessarily perfectly aligned).
$\rightarrow$ can we do something to infer a K-profile from these theoretical considerations? 
%
\begin{figure}
  \includegraphics[width=\textwidth]{../plot/mag_dir.pdf} 
  \caption{Total velocity and veering (in degrees) vs inner and outer height.
    Dashed lines show DNS data, thick lines are from semi-empirical theory.} 
\end{figure} 
%
\section{Conclusions}
%
Applications:
\begin{itemize}
\item reference-shear for neutral profile approaches(systematic!) $\rightarrow$ wind engineering! 
\item initial condition for LES/DNS to eliminate/minimize inertial oscillation in Benchmark simulations
\item
\end{itemize}

@@

\begin{subequations}
\begin{eqnarray}
  \left(\begin{matrix}
    \p_t U\\
    \p_t W  
  \end{matrix}\right)&=&\left(\begin{matrix}
     fW &+& \nu \p_z^2 U\\ 
    -f(U-G) &+& \nu \p_z^2 W
  \end{matrix}\right)\\ 
  \Rightarrow \partial_t (U+iW) &=& f(W-i(U-G))) + \nu \p_z^2(U+iW)
\end{eqnarray}
In stationary conditions, this system is solved by
\begin{eqnarray}
  \hat{u}(z) &=& U_{\infty} + e^{-\gamma z} \left[A \cos\gamma z + B \sin\gamma z\right]   \\
  \hat{w}(z) &=& W_{\infty} + e^{-\gamma z} \left[-A \sin\gamma z + B \cos\gamma z\right]
\end{eqnarray} 
\end{subequations}
where the constants $U_\infty$, $W_\infty$ set the top boundary condition and $A$ and $B$ set the bottom boundary condition. 
%
The most common boundary condition for a surface Ekman layer is $A=U_{\infty}=G$, $B=0$, and $W_{\infty}=0$.
%
The lower boundary condition, however, neglects the existence of the surface layer, and it appears reasonable to define
$A=c G$ where $c<1$ is a constant that icorporates the increased shear in the surface layer.
%
Given a 'matching height' $z_{match}$ and normalized matching height $\xi=\gamma z_\text{match}$ in the upper part of the inner layer, we can match the Ekman profile
to the inner layer by letting
%
\begin{eqnarray}
  \begin{matrix} 
    u(z_\text{match}) \equiv u_\text{match} &=& U_{\infty} + e^{-\gzm} \left [ A \cos\gzm + B\sin\gzm \right] \\
    w(z_\text{match}) \equiv w_\text{match} &=& W_{\infty} + e^{-\gzm} \left [-A \sin\gzm + B\cos\gzm \right]
  \end{matrix} 
\end{eqnarray}
\begin{eqnarray}
  \Rightarrow \left(\begin{matrix}
    u_\text{match}-U_{\infty} \\ 
    w_\text{match}-W_{\infty}
  \end{matrix}\right) = e^{-\gzm}\left(\begin{matrix}A \\ B \end{matrix}\right)\left(\begin{matrix}
    \cos\gzm &+ \sin\gzm \\ -\sin\gzm &+ \cos\gzm
  \end{matrix} \right) \\
\end{eqnarray}
Matching the profile at $\xi=0$, one obtains
$A = \Delta u_\text{match} $ and $B=-\Delta w_\text{match} $; and when the direction $Ox$ is aligned
with the geostrophic wind, we obtain the textbook-case $A=|\mathbf{G}|$ and $B=0$.

@@

\section{Matching the spanwise velocity profiles in the inner layer}
\label{app:log-coefficients}
The spanwise profile in vicinity of the surface is given by
$V/G=f_{V,\mathrm{visc}}\delta ^+$ with
\begin{subequations}
\begin{eqnarray}
  f_{V,\mathrm{visc}} &=& v_\mathrm{ref}\left(\omega_v z^+ -1 + e^{-\omega_v z^+}\right)\\
  f_{V,\mathrm{log}}   &=& a_\mathrm{log} + b_\mathrm{log} \log z^+ + c_\mathrm{log} z^+ 
\end{eqnarray}
\end{subequations}
Matching the profiles and gradient $z_0=10^+$ and the value at $z_1=0.3\delta^+$ yields
\begin{subequations} 
\begin{eqnarray}
  v_\mathrm{ref} \left(\omega_v z_{0} + e^{-\omega_v z_{0}}\right)
  & = v_{0}=& a_\mathrm{log} + b_\mathrm{log} \log z_{0} +c_\mathrm{log} z_{0}  \\
  &   v_{1}=& a_\mathrm{log} + b_\mathrm{log} \log z_{1} +c_\mathrm{log} z_{1} \\
  v_\mathrm{ref}\omega_z \left( 1 - e^{-\omega_z z_{0}}\right)
  & = d_{0}=& \frac{b_\mathrm{log}}{z_{10}} + c_\mathrm{log} 
\end{eqnarray}
\end{subequations} 
The gradient condition implies $b_\mathrm{log}=(d_{0} -c_\mathrm{log})z_{0}$, and yields
\begin{subequations}
\begin{eqnarray}
  %v_{0}&=& a_\mathrm{log} + z_{0}\left[ (d_0-c_\mathrm{log}) \log z_{0} +c_\mathrm{log}\right]\\
  v_0-z_0d_0\log z_0&=& a_\mathrm{log} + c_\mathrm{log} (z_0- z_0\log z_0) \\
  %v_1 &=& a_\mathrm{log} + z_0(d_0-c_\mathrm{log})\log z_1 +  c_\mathrm{log}z_1\\ 
  v_1-z_0d_0\log z_1 &=& a_\mathrm{log} +c_\mathrm{log} (z_1- z_0\log z_0)  \\
  \Rightarrow c_\mathrm{log}&=& \frac{ \Delta v - z_0d_0 \log z_1/z_0}{\Delta z} 
\end{eqnarray}
with $\Delta z=z_1-z_0$ and $\Delta v=v_1-v_0$.
%
Then, the coefficient $a_\mathrm{log}$ is estimated as 
\begin{eqnarray} 
  a_\mathrm{log} &=& v_0-z_0d_0\log z_0 -  \frac{ \Delta v - z_0d_0 \log z_1/z_0}{\Delta z}\left[
    z_0-z_0\log z_0 
    \right]. 
\end{eqnarray}
We note that $ \log(z_1/z_0) / (z_1-z_0) \rightarrow 0$ for large $z_1$, and as $z_1=0.3\delta^+$,
this implies that the second term in $c_\mathrm{log}$ only plays a role at low and intermediate $\RE$.
Then, $a_\mathrm{log}$ can be estimated as 
\begin{eqnarray}
  a_\mathrm{log} \simeq v_0 -z_0 \left[ d_0 \log  z_0 - \frac{\Delta v}{\Delta z} ( 1- \log z_0) \right] 
\end{eqnarray}
for large $\RE$. 
\end{subequations}

@@

  \end{array} \right. , 

@@

with $\Delta V = V_\text{outer}(z^-_\text{up})-V_\text{inner}(z^+_\text{low})$

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
